---
title: "Assessment 1.2"
author: '"Divya Kasturi s4654177'
date: "22/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Data Wrangling 
#created an r chunk to install package skimr and read the packages tidyverse and skimr
```{r}
#install.packages('skimr')
library(tidyverse)
library(skimr)

```

#a variable fastfood is used (as created in assessment1.1) to read the dataset fastfood.
```{r}
fastfood<-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

```
#used skim function to display the types of variables in the dataset. 
```{r}
fastfood%>%skim()

```
#displayed the number of observations for each restaurant
```{r}
fastfood%>%count(restaurant)

```
#Calculated  and displayed the average number of calories for each restaurant.

```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(average_calories=mean(calories))%>%
  ungroup()
```

#Created a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories` 

```{r}
fastfood%>%
  group_by(restaurant)%>%
  mutate(average_calories=mean(calories))%>%
  ungroup()
```
#Displayed the data vis of total fat per each type of restaurant. In this chunk of data viz geom_point is being used to display the observations and created scatter plots and It can be used to compare two categorical variables or one continuous and one categorical variable.
```{r}
fastfood%>%
  ggplot(aes(restaurant,total_fat))+
  geom_line()
  
```
# Displayed the count of observations per each type of restaurant.
```{r}

fastfood%>%count(restaurant)

```
#Added a variable to the dataset and  calculated  the maximum total fat per type of restaurant and call it `max_total_fat`

```{r}

fastfood%>%
  group_by(restaurant)%>%
  mutate(max_total_fat=max(total_fat))%>%
  ungroup()
  
  
```

#Used observations for Mcdonalds to plot sugar variable against protein with `geom_point()`
```{r}
fastfood%>%
  filter(restaurant=="Mcdonalds")%>%
  ggplot(aes(sugar,protein))+
  geom_point()

```


